Ecological network control

### 2018-05-23 paper/supp-info.Rmd
Finding all matchings section in supp info

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
bibliography: references.bib
---

@@

## Finding all possible maximum matchings

>>>>

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
bibliography: references.bib
---

@@

## Finding all possible maximum matchings {#all-maximum-matching}

The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of possibly many maximum matchings in a network. 
Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-maximum-matching-procedure)b and assign an identity to each of the links in the network.
We will call this bipartite representation *P*. 
We then construct the line graph of the alternative bipartite representation *L(P)* (Figure \@ref(fig:fig-all-maximum-matching)). 
Each node in *L(P)* represents a link in *P* and these are connected to each other if and only if they share a common node in *P*. 
We then calculate *H*, the complement graph of *L(P)* and identify all of its maximal cliques (Figure \@ref(fig:fig-all-maximum-matching)). 
Here some extra definitions are necessary. 
First, *H* is a graph with the same nodes as *L(P)* but that has a link between two nodes if and only if there is not a link in *L(P)*. 
Second, a clique is a subset of nodes such that all pairs of them are linked. 
Lastly, a maximal clique is a clique such that there are no cliques composed of more nodes [@Gutin2013]. 
In this example, there are two maximal cliques: the one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
The final step is then to map these cliques onto the original network to obtain all possible maximal cardinality matchings as shown in Figure \@ref(M-fig:fig-control-configuration) in the main text.

```{r}
drake::loadd(fig_all_matching)
```

```{r fig-all-maximum-matching, fig.height=fig_all_matching$height, fig.width=fig_all_matching$width,fig.cap = "Finding all possible maximum matchings. From left to right: alternative bipartite representation of the directed network in Figure \\@ref(fig:fig-maximum-matching-procedure)a.  Line graph of the network. Complement of the network. The two maximal cliques are shown in dark purple."}
replayPlot(fig_all_matching$plot)
```

To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)). 
This network is composed of 19 species of which three are non-invasive plants and the other 16 are pollinators. 
The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence are classified as driver nodes that require external intervention. 
At the same time, both plants in the community, *Heracleum sphondylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.

```{r}
drake::loadd(fig_small_network)
```

```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "Illustration of the procedure with an empirical community. The visitation network (top), the number of visits between species pairs is shown on each link. The directed network in which the direction of control is determined based on the mutual dependences (middle). One of the possible maximum matchings of this network (bottom)."}
replayPlot(fig_small_network$plot)
```
